\frb: Very Large Array Burst Properties and Implications for Overall FRB Population

### 2016-11-15 repeater-vladata.tex
working through vla observing info

\section{Observations}
\subsection{VLA}

@@

% from the first paper
During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin. The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information. Each frequency channel was coherently dedispersed to 557~\dmu, thereby eliminating intra-channel dispersion smearing. PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.

>>>>

\section{Observations}
The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb with the VLA. We ultimately settled on a strategy based on simultaneous observing between the VLA and Arecibo observatories with other observatories added on a best-effort basis. The hope was that Arecibo could be used to define times of bursts for which we could selectively search with the VLA. This would reduce the trials factor that limited sensitivity and potentially provide detections at multiple independent bands. Below, we summarize these observations, with a focus on those conducted simultaneous with VLA burst detections from \frb.

\subsection{VLA}
The \frb observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz. In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in coordination with Arecibo. We concluded with a new, 40~hr, coordinated campaign from August through September 2016. In this last campaign, the first 34 hours of VLA observations were made at 3.0~GHz, while the last 6 hours were observed at 6~GHz.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}. To maximize sensitivity, the channel spectral width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth. The total bandwidth at L (1.4~GHz), S (3.0~GHz), and C (6.0~GHz) bands was 256~MHz, 1.0~GHz, and 2.0~GHz, respectively.

@@

% from the first paper
During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin. The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information. Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing. PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.
